Understanding the technological transition based on cultural transmission biases during the Late Pleistocene in Korea

### 2020-05-26 analysis/paper/paper.Rmd
add a few words for commit/push
stash

biological concept to archaeological usage: (Richerson and Boyd 1992)

Cultrual evolution that archaeologists adapted has three sub-categories: human behavioral ecology, phylogenetics and cultural transmission theory (Garvey 2018). Among them, we apply models and methods of cultural tranmssion to understand the technological change and socio cultural contexts.

@@

The transmission is subject to biases that result from different social contexts. Boyd and Richerson (1985) and Henrich and McElreath (2003) have defined many of these biases, including ‘guided variation’ (where individuals learn new behaviors and then modify them through trial and error), ‘content-based bias’ (where some aspect of the transmitted instructions, such as cultural preferences, makes them more likely to be adopted), ‘frequency-based bias’ (where an individual is biased to choose particular instructions based on their perceived frequency in the population, such as extremely popular or rare instructions), and ‘model-based bias’ (where a variant is transmitted because of its association with other attributes, such as the prestige or skill of other individuals).

>>>>

need to add 'biological concept to archaeological usage': (Richerson and Boyd 1992)

Cultural evolution that archaeologists adapted has three sub-categories: human behavioral ecology, phylogenetics and cultural transmission theory (Garvey 2018). Among them, we apply models and methods of cultural transmission to understand the technological change and socio cultural contexts.

@@

The transmission is subject to biases that result from different social contexts. Boyd and Richerson (1985) and Henrich and McElreath (2003) have defined many of these biases, including ‘guided variation’ (where individuals learn new behaviors and then modify them through trial and error), ‘content-based bias’ (where some aspect of the transmitted instructions, such as cultural preferences, makes them more likely to be adopted), ‘frequency-based bias’ (where an individual is biased to choose particular instructions based on their perceived frequency in the population, such as extremely popular or rare instructions), and ‘model-based bias’ (where a variant is transmitted because of its association with other attributes, such as the prestige or skill of other individuals). <!-- add some description of experimental and ethnographic evidence that these biases are real, some of this not archaeological, e.g. https://www.pnas.org/content/116/14/6726  -->
